\bibliographystyle{splncs04}
\begin{thebibliography}{XXX}
\bibitem{hyperledger_OpenStack} Kim Y., Park J. Hybrid decentralized PBFT Blockchain Framework for OpenStack message queue //Human-centric Computing and Information Sciences. – 2020. – T. 10. – №. 1. – C. 31.
\bibitem{pub_sub}  Ghaemi S. et al. A pub-sub architecture to promote blockchain interoperability //arXiv preprint arXiv:2101.12331. – 2021.
\bibitem{healthcare_concept} Gupta S., Yadav B., Gupta B. Security of IoT-based e-healthcare applications using blockchain //Advances in Blockchain Technology for Cyber Physical Systems. – Cham : Springer International Publishing, 2022. – C. 79-107.
\bibitem{bbs} Wang S. et al. BBS: A secure and autonomous blockchain-based big-data sharing system //Journal of Systems Architecture. – 2024. – T. 150. – C. 103133.
\bibitem{probes} Jia X. et al. Cross‐organisational data sharing framework based on blockchain‐probes //IET Networks. – 2023. – T. 12. – №. 2. – C. 77-85.
\bibitem{peer_to_peer} Peng S. et al. A peer-to-peer file storage and sharing system based on consortium blockchain //Future Generation Computer Systems. – 2023. – T. 141. – C. 197-204.
\bibitem{multi_level_IoV} Lin H. Y. Secure Data Transfer Based on a Multi-Level Blockchain for Internet of Vehicles //Sensors. – 2023. – T. 23. – №. 5. – C. 2664.
\bibitem{pbft_and_raft} Bogdanov A. et al. Combining PBFT and Raft for Scalable and Fault-Tolerant Distributed Consensus //Physics of Particles and Nuclei. – 2024. – T. 55. – №. 3. – C. 418-420.
\bibitem{smart_transport_concept} Bagga P., Das A. K. Blockchain for Smart Transport Applications //Advances in Blockchain Technology for Cyber Physical Systems. – Cham : Springer International Publishing, 2022. – C. 125-154.
\bibitem{fog_nodes} Priyadarshini R., Malarvizhi N. Secured data transfer between fog nodes using blockchain //Proceedings of the 2nd International Conference on Computational and Bio Engineering: CBE 2020. – Springer Singapore, 2021. – C. 417-422. 
\bibitem{bbas_iov} Bagga P. et al. Blockchain-based batch authentication protocol for Internet of Vehicles //Journal of Systems Architecture. – 2021. – T. 113. – C. 101877.
\bibitem{oil_and_gas} Wang Y. Y., Huang S., Yu X. An oil and gas big data sharing model based on blockchain technology //IOP Conference Series: Earth and Environmental Science. – IOP Publishing, 2021. – T. 651. – №. 3. – C. 032105.
\bibitem{birds} Yang H. et al. A Research on the Sharing Platform of Wild Bird Data in Yunnan Province Based on Blockchain and Interstellar File System //Sensors. – 2022. – T. 22. – №. 18. – C. 6961.
\bibitem{roadside_unit} Xu Z. et al. A blockchain-based roadside unit-assisted authentication and key agreement protocol for internet of vehicles //Journal of Parallel and Distributed Computing. – 2021. – T. 149. – C. 29-39.
\bibitem{blockchain_survey} Song R. et al. A survey of blockchain-based schemes for data sharing and exchange //IEEE Transactions on Big Data. – 2023.
\bibitem{BCPPA} Lin C. et al. BCPPA: A blockchain-based conditional privacy-preserving authentication protocol for vehicular ad hoc networks //IEEE Transactions on Intelligent Transportation Systems. – 2020. – T. 22. – №. 12. – C. 7408-7420.
\bibitem{proof_of_transaction} Ai, Z., Cui, W. (2022). A proof-of-transactions blockchain consensus protocol for large-scale IoT. IEEE Internet of Things Journal. https://doi.org/10.1109/JIOT.2021.3108627
\end{thebibliography}
\clearpage